### 2016-02-29 ch02-qlogms/excitation-design.tex
Add some TODOs
Fix styles + some comments of Johan CH02

\subsection{Approach in this chapter}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
                 0 & \ddots & 0 \\
                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}

@@

  The obtained FRF is then fitted to the transfer function model \eqref{eq:excitation:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT~\citep{FDIDENT} for \MATLAB.
  This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
  %TODO: add formulas with cost function etc.
  To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.

@@

  \begin{remark}
  All simulations  have been repeated as well by fitting with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
  The observed results were similar and hence are not elaborated further in this text.
  For more information, please refer to \citep{Larsson2012SYSID}.
  \end{remark}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

@@

    The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
    According to its manual \citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis}~\citep{FDIDENT}.
    The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
      \label{fig:excitation:measurements}
    \end{figure}

>>>>

\subsection{General purpose robust excitation signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & \deemph{0} & \deemph{0}\\
                 \deemph{0} & \ddots & \deemph{0} \\
                 \deemph{0} & \deemph{0} & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}

@@

  The obtained FRF is then fitted to the transfer function model \eqref{eq:excitation:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT~\citep{FDIDENT} for \MATLAB.
  This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
  %TODO: add formulas with cost function etc.
  To improve convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.

@@

  \begin{remark}
  All simulations  have been repeated as well by fitting with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
  The observed results were similar and hence are not elaborated further in this text.
  For more information, please refer to~\citep{Larsson2012SYSID}.
  \end{remark}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

@@

    The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
    According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
    A first guess to realize such a filter is a sixth-order Chebyshev band-pass filter of Type I~\citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
    %TODO: datasheet FRF?, pzmap with \damping shown, evt. tabel: per pool-paar: \wn ifv \wc, \damping
    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis}~\citep{FDIDENT}.
    The initial estimate was a sixth-order band-pass type I Chebyshev filter~\citep{Zverev1967} that conformed to the information given in the datasheet~\citep{datasheet_bk1613} to aid convergence to a good optimum.

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
    \TODO{use styles from above}
      \label{fig:excitation:measurements}
    \end{figure}

### 2016-02-29 config/styles.inc.tex
Add some TODOs
Fix styles + some comments of Johan CH02

\pgfplotsset{compat=newest}
%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots

% \def\thisDir{.}

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}

\pgfplotsset{legendAbovePlot/.style={legend style={at={(0.5,1.025)},anchor={south},nodes=right,legend columns=-1,font=\footnotesize,draw=none,/tikz/every even column/.append style={column sep=1em}}}}

@@

\definecolor{model}{named}{blue}
\definecolor{truesys}{named}{TangoAluminium5}
% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper

@@

@@

%% marker styles
  \definecolor{bwfill}{named}{TangoAluminium1}
  \definecolor{bwline}{named}{TangoAluminium5}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}

@@

\pgfplotsset{linmsgrid/.style={color=linms,gridline,mark=square*,mark options={solid}}}
\pgfplotsset{logmsgrid/.style={color=logms,gridline,mark=*,mark options={solid}}}
\pgfplotsset{clogmsgrid/.style={color=clogms,gridline,mark size=2pt,mark=x,mark options={solid}}}
\pgfplotsset{plogmsgrid/.style={color=plogms,gridline,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}

\pgfplotsset{linms/.style={color=linms}}
\pgfplotsset{clogms/.style={color=clogms}}
\pgfplotsset{rlogms/.style={color=rlogms}}
\pgfplotsset{qlogms/.style={color=qlogms}}
\pgfplotsset{plogms/.style={color=plogms}}

\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
\pgfplotsset{truesys/.style={color=tangogrey,line width=0.9pt}}

@@

\pgfplotsset{linmsmeas/.style={color=linms,densely dashed,line width=0.7pt}}
\pgfplotsset{qlogmsmeas/.style={color=qlogms,densely dotted,line width=0.7pt}}
\pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}
\pgfplotsset{plogmsmeas/.style={color=plogms,solid,line width=0.7pt}}

@@

\pgfplotsset{sigmalinms/.style={linms,connectline}}
\pgfplotsset{sigmaqlogms/.style={qlogms,connectline}}
\pgfplotsset{sigmaclogms/.style={clogms,connectline}}
\pgfplotsset{sigmaplogms/.style={plogms,connectline}}

@@

\pgfplotsset{linmsgrid/.style={ycomb,color=linms,solid,line width=0.7pt,mark size=1pt,mark=square*,mark options={solid}}}
\pgfplotsset{logmsgrid/.style={ycomb,color=logms,solid,line width=0.7pt,mark size=1pt,mark=*,mark options={solid}}}
\pgfplotsset{clogmsgrid/.style={ycomb,color=clogms,solid,line width=0.7pt,mark size=2pt,mark=x,mark options={solid}}}
\pgfplotsset{plogmsgrid/.style={ycomb,color=plogms,solid,line width=0.7pt,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}

\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
\pgfplotsset{truesys/.style={color=truesys,line width=1.0pt}}

\newcommand{\linmsmarker}{mark=square,mark options={solid}}
\newcommand{\qlogmsmarker}{mark=triangle,mark options={solid}}
\newcommand{\clogmsmarker}{mark=x,mark size=10pt,mark options={solid}}

@@

\pgfplotsset{sigmalinms/.append style={color=sigmalinms,solid,line width=0.8pt}}
\pgfplotsset{sigmaqlogms/.append style={color=sigmaqlogms,solid,line width=0.8pt}}
\pgfplotsset{sigmaclogms/.append style={color=sigmaclogms,solid,line width=0.8pt}}

\pgfplotsset{biaslinms/.style={color=biaslinms,only marks,mark=x,mark options={solid}}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,only marks,mark=triangle,mark options={solid,rotate=180}}}
\pgfplotsset{biasclogms/.style={color=biasclogms,only marks,mark=o,mark options={solid}}}

@@

\pgfplotsset{dbavar/.style={color=dbacolor,solid,line width=1.0pt}}
\pgfplotsset{dbbvar/.style={color=dbbcolor,solid,line width=1.0pt}}
\pgfplotsset{dbcvar/.style={color=dbccolor,solid,line width=1.0pt}}
\pgfplotsset{dbdvar/.style={color=dbdcolor,solid,line width=1.0pt}}

\pgfplotsset{dbamin/.style={color=dbacolor,dashed,line width=1.0pt}}
\pgfplotsset{dbbmin/.style={color=dbbcolor,dashed,line width=1.0pt}}
\pgfplotsset{dbcmin/.style={color=dbccolor,dashed,line width=1.0pt}}
\pgfplotsset{dbdmin/.style={color=dbdcolor,dashed,line width=1.0pt}}

\pgfplotsset{dbamax/.style={color=dbacolor,solid,line width=1.0pt,mark=x ,mark options={solid}}}
\pgfplotsset{dbbmax/.style={color=dbbcolor,solid,line width=1.0pt,mark=o ,mark options={solid}}}
\pgfplotsset{dbcmax/.style={color=dbccolor,solid,line width=1.0pt,mark=square  ,mark options={solid}}}
\pgfplotsset{dbdmax/.style={color=dbdcolor,solid,line width=1.0pt,mark=triangle,mark options={solid}}}

@@

\pgfset{number format/1000 sep={\,}}

@@

\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

@@

\pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}

@@

%%

>>>>

\pgfplotsset{compat=newest}

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={at={(0.5,1.025)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}

%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots
\pgfplotsset{legendAbovePlot/.style={legend style={at={(0.5,1.025)},anchor={south},nodes=right,legend columns=-1,font=\footnotesize,draw=none,/tikz/every even column/.append style={column sep=1em}}}}

%TODO: avoid duplicated styles !!

%% Number formatting
\pgfset{number format/1000 sep={\,}}

@@

\definecolor{model}{named}{black}
\definecolor{truesys}{named}{TangoAluminium5}
% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper

@@

  \definecolor{bwfill}{named}{TangoAluminium1}
  \definecolor{bwline}{named}{TangoAluminium5}

%% Marker sizes
\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

@@

%% marker styles

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}

\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
\pgfplotsset{truesys/.style={color=tangogrey,line width=1pt}}
\pgfplotsset{mainsys/.style={color=black,line width=1pt}}
\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}

@@

\pgfplotsset{linmsgrid/.style={color=linms,gridline,linmsmarker}}
\pgfplotsset{logmsgrid/.style={color=logms,gridline,logmsmarker}}
\pgfplotsset{clogmsgrid/.style={color=clogms,gridline,clogmsmarker}}
\pgfplotsset{plogmsgrid/.style={color=plogms,gridline,plogmsmarker}}

@@

%TODO: change these styles?
\pgfplotsset{linmsmeas/.style={color=linms,densely dashed,line width=0.7pt}}
\pgfplotsset{qlogmsmeas/.style={color=qlogms,densely dotted,line width=0.7pt}}
\pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}
\pgfplotsset{plogmsmeas/.style={color=plogms,solid,line width=0.7pt}}

@@

\pgfplotsset{sigmaline/.style={solid,line width=0.8pt}}
\pgfplotsset{sigmalinms/.append style={linms,sigmaline}}
\pgfplotsset{sigmaqlogms/.append style={qlogms,sigmaline}}
\pgfplotsset{sigmaclogms/.append style={clogms,sigmaline}}
\pgfplotsset{sigmaplogms/.append style={plogms,sigmaline}}

\pgfplotsset{biasline/.style={densely dotted}}
\pgfplotsset{biaslinms/.style={color=biaslinms,linmsmarker,biasline}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,qlogmsmarker,biasline}}
\pgfplotsset{biasclogms/.style={color=biasclogms,clogmsmarker,biasline}}

@@

@@

@@

@@

@@

@@

%TODO: redefine this thingie for LRM chapters
% \pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}

@@
